Memory-Efficient Mixed-Precision Implementations\\for Robust Explicit Model Predictive Control

### 2019-04-12 emsoft-2019/Error_Analysis.tex
comment on section 4

In this section, we present our error analysis assuming that a fixed-point word lengths is given.
Then in the next section, we explain our optimization algorithm which determines suitable word
lengths fully automatically.% in~\autoref{sec:Controller_Synthesis}.
While we do not employ the error analysis independently of the controller and
precision synthesis, we note that it is an alternative way of bounding errors to
existing methods~\cite{imperialrmpc}, which phrase the roundoff error computation as a (relaxed)
mixed integer programming problem.
%\Sadegh{Alternative in what sense? What is the major difference between our analysis and \cite{imperialrmpc}?}

@@

Due to the affinity of function
$v_{i}-v_{j}$, and because we defined the tube as a convex region surrounding the corresponding hyperplane, it suffices
to evaluate the function only at the corner points of the tube, and keep the
result with the maximal magnitude. 
To evaluate the incorrect region selection error across
the corner points, we need to first locate the corner points as well as all the
regions which share those corner points. 
Each region $R_i$ is represented by a set of contraints. We first extract the
set of vertices of $R_i$ using the open source Matlab library
$\mathit{lcon2vert}$~\cite{??}.
For each computed vertex $v_i$, we compute a $n-D$
hypercube with the edge length of $2 \varepsilon$. 
Each of the $2^n$ vertices of this hypercube is counted as a corner point, on which
we evaluate $\|u_i - u_j\|$.

@@

% The approximation error and the precision tuning for both borders and active
% functions are computed in Daisy. $\varepsilon_{Q}$ is given in input to the
% analysis. After we compute the incorrect region in MATLAB we obtain the value
% for max error $err(v_{i})$ from (8). Then we give the errors and the vectors F,G
% and H,K in input to Daisy. We used Daisy as a verification tool: we provide in
% input the expression we want to quantize (e.g. $\mathcal{R}_{i}$) together with
% the error bound we can tolerate (e.g. $\varepsilon_{Q}$), and Daisy returns a
% precision configuration (uniform or mixed) such that the input error is
% satisfied. The way it finds the right configuration for uniform precision is the
% following: it starts by checking whether the input expression, quantized in
% unary uniform precision (1bit), introduces an error bounded by the input error.
% If this is not the case, Daisy increases the precision format by 1 bit and check
% whether the error now is satisfied. This unary increment runs inside a loop that
% terminates when the first valid format is matched. This uniform word-length is
% going to be the baseline for the mixed-precision tuning phase. The
% mixed-precision algorithm keeps a list of variables to quantize, and collects
% different candidate configurations that satisfy the input error. It returns the
% best configuration based on the evaluation of a quality function.

>>>>

In this section, we present our error analysis assuming that a fixed-point word lengths is given.
Then in the next section, we explain our optimization algorithm which determines suitable word
lengths fully automatically.
% in~\autoref{sec:Controller_Synthesis}.
While we do not employ the error analysis independently of the controller and
precision synthesis, we note that it is an alternative way of bounding errors to
existing methods~\cite{imperialrmpc}, which phrase the roundoff error computation as a (relaxed)
mixed integer programming problem.
%\Sadegh{Alternative in what sense? What is the major difference between our analysis and \cite{imperialrmpc}?}

@@

Due to the affinity of function
$v_{i}-v_{j}$, and because we defined the tube as a convex region surrounding the corresponding hyperplane, it suffices
to evaluate the function only at the corner points of the tube, and keep the
result with the maximal magnitude. 
To evaluate the incorrect region selection error across
the corner points, we need to first locate the corner points as well as all the
regions which share those corner points. 
Each region $R_i$ is represented by a set of contraints. We first extract the
set of vertices of $R_i$ using the open source Matlab library
$\mathit{lcon2vert}$~\cite{lcon2vertMatlab}.
For each computed vertex $v_i$, we compute a $n-D$
hypercube with the edge length of $2 \varepsilon$. 
Each of the $2^n$ vertices of this hypercube is counted as a corner point, on which
we evaluate $\|u_i - u_j\|$.

@@

\textcolor{red}{Sadegh: This is long comment on the content of this section. I cannot figure out how this line of reasoning is mapped to the implementation. We can discard my comment given that we are close to the deadline.}

\Sadegh{
I don't agree that we should add $\varepsilon_{A/D}$ and $\varepsilon_Q$ together. I understand that the implementation is done according to this, but I think we need to multiply $\varepsilon_{A/D}$ by the maximum norm of the coefficients $F_i$ in the controller. There are three approximations:
\begin{itemize}
\item using the quantized measured state $\hat x$ instead of the actual state $x$. We assume $\|x - \hat x\|\le \varepsilon_{A/D}$.
\item using $\hat H_i,\hat K_i$ which are the quantized versions of $H_i,K_i$ with $p$ bits precision. This is related to the boundaries of the regions.
\item using $\hat F_i,\hat G_i$ which are the quantized versions of $F_i,G_i$ with $p$ bits precision. This is related to the affine functions.
\end{itemize}
Let me define the sets $\mathcal H := \{H_i,K_i,i=1,2,\ldots, P\}$ and $\mathcal F:=\{F_i,G_i,i=1,2,\ldots, P\}$. Similarly, we define $\hat{\mathcal H}$ and $\hat{\mathcal F}$.
The controller (which is a piecewise affine function) can be written as the parametric function $\kappa(\mathcal H,\mathcal F,x)$. Our main goal is to make sure that
$$\|\kappa(\mathcal H,\mathcal F,x)-\kappa(\hat{\mathcal H},\hat{\mathcal F},\hat x)\|\le \Delta,\quad \forall x\in\mathcal X_{\mathsf s}.$$
We use tirangle these inequality:
\begin{align*}
\|\kappa(\mathcal H,\mathcal F,x)-\kappa(\hat{\mathcal H},\hat{\mathcal F},\hat x)
\|\le&\|\kappa(\mathcal H,\mathcal F,x)-\kappa(\hat{\mathcal H},\mathcal F,\hat x)\|\\
+&\|\kappa(\hat{\mathcal H},\mathcal F,\hat x)-\kappa(\hat{\mathcal H},\hat{\mathcal F},\hat x)\|.
\end{align*}
The second term is exactly what we have in section 4.2 (error in the evaluation of the affine function).
The first term can be further decomposed as
\begin{align*}
\|\kappa(\mathcal H,&\mathcal F,x)-\kappa(\hat{\mathcal H},\mathcal F,\hat x)\|\\
&\le \|\kappa(\mathcal H,\mathcal F,x)-\kappa(\mathcal H,\mathcal F,\hat x)\|+
 \|\kappa(\mathcal H,\mathcal F,\hat x) - \kappa(\hat{\mathcal H},\mathcal F,\hat x)\|\\
&\le \max_i\{\|F_i\|_2\}\|x-\hat x\| + \varepsilon_Q\\
& \le \max_i\{\|F_i\|_2\}\varepsilon_{A/D}+ \varepsilon_Q.
\end{align*}
The error $\varepsilon_{A/D}$ shows itself in the output of the controller by being amplified with the Lipschitz constant of the function which is $\max_i\{\|F_i\|_2\}$. 
As far as I can tell, $\varepsilon_{A/D}$ doesn't have anything to do with $\varepsilon_Q$. The computation of $\varepsilon_Q$ should be only with respect to the use of $\hat{\mathcal H}$ instead of $\mathcal H$ in the evaluation of constraints for the same value $\hat x$.
}
% The approximation error and the precision tuning for both borders and active
% functions are computed in Daisy. $\varepsilon_{Q}$ is given in input to the
% analysis. After we compute the incorrect region in MATLAB we obtain the value
% for max error $err(v_{i})$ from (8). Then we give the errors and the vectors F,G
% and H,K in input to Daisy. We used Daisy as a verification tool: we provide in
% input the expression we want to quantize (e.g. $\mathcal{R}_{i}$) together with
% the error bound we can tolerate (e.g. $\varepsilon_{Q}$), and Daisy returns a
% precision configuration (uniform or mixed) such that the input error is
% satisfied. The way it finds the right configuration for uniform precision is the
% following: it starts by checking whether the input expression, quantized in
% unary uniform precision (1bit), introduces an error bounded by the input error.
% If this is not the case, Daisy increases the precision format by 1 bit and check
% whether the error now is satisfied. This unary increment runs inside a loop that
% terminates when the first valid format is matched. This uniform word-length is
% going to be the baseline for the mixed-precision tuning phase. The
% mixed-precision algorithm keeps a list of variables to quantize, and collects
% different candidate configurations that satisfy the input error. It returns the
% best configuration based on the evaluation of a quality function.
